\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Raghul Asokan}}\\
	Chennai, India $\cdot$ mailcorahul@gmail.com $\cdot$ +91 9566063156 $\cdot$ github.com/mailcorahul\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Anna University(SSNCE)}\hfill Chennai, India\\
Bachelor\textquotesingle{}s in Computer Science \textit{GPA: 8.6} \hfill Aug 2012 - May 2016\\
\vspace{2mm}
\textbf{Marian Mat. Hr. Sec. School}\hfill Chennai, India\\
Class XII State Board, 97\% \hfill June 2011 - April 2012\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Zoho Corporation} \hfill Chennai, India\\
\textit{Deep Learning Engineer at ZLabs} \hfill June 2016 | Present\\
\vspace*{2mm}
{\textbf{Receipt Digitizer}} {\sl Keras, OpenCV, Numpy} \\
Developed an Optical Character Recognition(OCR) pipeline using Neural Networks for extracting useful receipt information such as amount, date, mode of payment, currency. This end-to-end pipeline consists of various stages such as Orientation Detection, Text Detection, Text Recognition and Information Retrieval.\\            
            \begin{itemize}
                \itemsep-0.5em
                \item Text Recognition architectures:CNN + BLSTM + CTC, CNN + CTC(Rosetta).
                \item Text Recognition Dataset: Synthetically generated word images using various fonts, backgrounds and image transformations.
                \item Single Word Accuracy(SWA) of 85\%.
            \end{itemize}

\header{Projects}
{\textbf{Subtitle Generator/Video Summarizer}} {\sl OpenCV, DeepSpeech} \hfill \textit{https://github.com/mailcorahul/subs\_generator}\\
This subtitle generator pipeline consists of multiple stages such as Audio extraction, Voice Activity Detection, Segmentation, Speech-to-Text using Deep Speech and a Text Summarizer.\\
\vspace*{2mm}
{\textbf{Image Super-Resolution Using Deep Convolutional Networks}}\hfill \textit{https://github.com/mailcorahul/super\_resolution}\\
A PyTorch implementation of the paper for enhancing the quality of word images used for OCR Word Recognition.\\
    \begin{itemize}
        \itemsep-0.5em
        \item Dataset used: Synthetically generated receipt word images.
        \item Accuracy - Average PSNR: 19.92 dB
    \end{itemize}

\vspace*{2mm}
{\textbf{Other Computer Vision Projects}} \\ \textit{https://github.com/mailcorahul/computer\_vision}\\

    \begin{itemize}
        \itemsep-0.5em
        \item Character Recognition(94 classes) using CNN.Synthetic character dataset using 9217 fonts, Accuracy - 95\%.
        \item Text Detection using Maximally Stable Extremal Regions with increased recall and performance.
        \item Boundary Detection in Receipts using Structured Forests and Hough Line Transform.\\
    \end{itemize}
\vspace*{2mm}
{\textbf{Cloud Service Ranking and Selection - A Genetic Algorithm Approach(B.E Project)}}\hfill \textit{https://github.com/mailcorahul/GA}\\
This project focuses on a system which uses an optimization algorithm - Genetic Algorithm for cloud service selection based on parameters such as processor speed, cost, RAM etc.\\
\vspace*{2mm}

\header{Skills}
\begin{tabular}{ l l }
    Programming Languages: & C, C++, Python, Java                                   \\
    Deep Learning:         & Numpy, OpenCV, PyTorch, Keras                          \\
    Web:                   & HTML, CSS, Javascript, jQuery, Apache Tomcat, CherryPy \\
    Platforms:             & Linux, Windows                                         \\
\end{tabular}
\vspace{2mm}

\header{Awards}
\textbf{Obtained Merit Scholarship for the year 2013-2014 for the securing second rank in Anna University examination.}\\

\vspace*{2mm}
\textbf{Won first place in Coding contest in Reboot, a National level Technical Symposium organized by MCA department held at SSN College of Engineering.}\\

\vspace*{2mm}
\textbf{Secured third place in Zia Hackathon 2018 - A Machine Learning Hackathon held at Zoho Corporation.}\\

\vspace*{2mm}

\ 
\end{document}